### 2019-10-29 tesis_hiram/Chapter4/chapter4.tex
nuevo

	\section{Likelihood and fit procedure}
	The likelihood function is the product of Poisson probabilities for all bins of the BDT distribution. The likelihood function has the form
	\begin{align}
		L(\mu,\alpha)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)} \prod_{k=1}^M e^{\frac{-\alpha^2_k}{2}}
	\end{align}
	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, µ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
	$b_j$ is the sum of different background processes $k$
	\begin{align}
		b_j=\sum_k^M b_j^k(1+ \alpha_k \sigma_k)
	\end{align}
	$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. $\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.
	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$. The minimization is performed by using the package ROOFIT \cite{roofit}. In the figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models. \\
	%log es usado para evitar valores extremadamente pequenos debido a los productos de los exponenciales
	%negativo es para hacer una minimizacion, positivo es maximizacion
	As mentioned before, for the $k_t$=-1 the number of events for signal is more than ten times compared to SM. This improves the sensitivity to the signal. Due to the small number of signal events the uncertainty for the SM is large compared to the $k_t$=-1 scenario, where the uncertainty is around 50$\%$. In this analysis only the signal is affected by the change $k_t$=1 (SM) $\rightarrow$ $k_t=-1$, therefore the backgrounds remain the same.

>>>>

	\section{Likelihood and fit procedure}
	The likelihood function is the product of Poisson probabilities for all bins of the BDT distribution. The likelihood function has the form
	\begin{align}
		L(\mu,\alpha)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)} \prod_{k=1}^M e^{\frac{-\alpha^2_k}{2}}
	\end{align}
	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, $\mu$ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
	$b_j$ is the sum of different background processes $k$
	\begin{align}
		b_j=\sum_k^M b_j^k(1+ \alpha_k \sigma_k)
	\end{align}
	$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. $\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.
	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$. The minimization is performed by using the package ROOFIT \cite{roofit}. In the figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models. \\
	%log es usado para evitar valores extremadamente pequenos debido a los productos de los exponenciales
	%negativo es para hacer una minimizacion, positivo es maximizacion
	As mentioned before, for the $k_t$=-1 the number of events for signal is more than ten times compared to SM. This improves the sensitivity to the signal. Due to the small number of signal events the uncertainty for the SM is large compared to the $k_t$=-1 scenario, where the uncertainty is around 50$\%$. In this analysis only the signal is affected by the change $k_t$=1 (SM) $\rightarrow$ $k_t=-1$, therefore the backgrounds remain the same.
